---
title: "Explore Difference in Protected Area"
author: "Benedito Chou"
date: '2019-03-29'
output: html_document
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)

```

## Setup Library
Install these packages if neccessary.
```{r project_setup, message = FALSE, warning = FALSE}

library(readr)
library(gamlss)
library(tidyr)
library(knitr)
library(DT)
library(dplyr)
library(stringr)
library(scales)
library(broom)
library(ggplot2)
library(ggbeeswarm)

```

## Data Preparation

### Load Data
Load the data imported, processed and saved from "data wrangle change score centroid and map data.R".
```{r}

load("processed_data v3.RData")

```

### Prepare Data

Keep distinct records within each time point only because keeping all pairwise records will inflate the number of observations in time 1 and 2.
```{r}

data_long <- distinct(merged_data_record_all_long, tribe, time, FIPS, .keep_all = TRUE)

```

Create data.frame to include only tribes with time 1 and 2 data.
```{r}

data_t1and2_long <- filter(data_long, tribe %in% tribes_time1and2_lst$tribe)

```

**Check Data**

First, confirm the data is correct, each tribe should have 2 summarized records in total, one for time 1 and one for time 2, so the resulted data.frame should has 0 row.
```{r}
t1and2_lst <- group_by(data_t1and2_long, tribe, time) %>% 
  count() %>%
  ungroup() %>%
  group_by(tribe) %>%
  count() %>%
  filter(n < 2)

nrow(t1and2_lst)
```


## Exploratory Analyses

### Plot Proportion of Protected Area by Time
### All Tribes, including those with time 1 or time 2 data only

* The distribution of proportion of protected area in time 1 and time 2 is skewed to the right and is zero-inflated with notable outliers.
* The distirbution of proportion of protected area is in general higher in time 2 compared to time 1.

```{r, message = FALSE, warning = FALSE}

ggplot(data_long, aes(p_all, fill = time)) +
  facet_grid(rows = vars(time), scales = "free") +
  geom_histogram(position = "dodge", binwidth = .05) +
  theme_minimal()

ggplot(data_long, aes(time, p_all, colour = time)) +
  geom_boxplot() +
  geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
  theme_minimal()

```

#### Look at only those with protected area only

* The distirbution of proportion of protected area is in general higher in time 2 compared to time 1 for tribes in counties with protected area only.

```{r, message = FALSE, warning = FALSE}

data_long_p_all_only <- filter(data_long, p_all > 0)

ggplot(data_long_p_all_only, aes(p_all, fill = time)) +
  facet_grid(rows = vars(time), scales = "free") +
  geom_histogram(position = "dodge") +
  theme_minimal()

ggplot(data_long_p_all_only, aes(time, p_all, colour = time)) +
  geom_boxplot() +
  geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
  theme_minimal()

```

### Tribes with both time 1 or time 2 data

* The distribution of proportion of protected area in time 1 and time 2 is skewed to the right and is zero-inflated with notable outliers.
* The distirbution of proportion of protected area is in general higher in time 2 compared to time 1.

```{r, message = FALSE, warning = FALSE}

ggplot(data_t1and2_long, aes(p_all, fill = time)) +
  facet_grid(rows = vars(time), scales = "free") +
  geom_histogram(position = "dodge", binwidth = .05) +
  theme_minimal()

ggplot(data_t1and2_long, aes(time, p_all, colour = time)) +
  geom_boxplot() +
  geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
  theme_minimal()

```

#### Look at only those with protected area only

* The distirbution of proportion of protected area is in general higher in time 2 compared to time 1 for tribes in counties with protected area only.

```{r, message = FALSE, warning = FALSE}

data_t1and2_long_p_all_only <- filter(data_t1and2_long, p_all > 0)

ggplot(data_t1and2_long_p_all_only, aes(p_all, fill = time)) +
  facet_grid(rows = vars(time), scales = "free") +
  geom_histogram(position = "dodge") +
  theme_minimal()
  
ggplot(data_t1and2_long_p_all_only, aes(time, p_all, colour = time)) +
  geom_boxplot() +
  geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
  theme_minimal()

```


## Test for Significant Difference

### (1) Test for significant difference at the aggregate level

* Zero-inflated Beta Model is a parametric test for comparing proportion data. Unlike t-test or ANOVA, this test is appropriate for porportion data that are bound by 0 to 1, with excessive 0 values.
* Use Zero-inflated Beta Model because the outcome proportion of protected area is a proportion mesure.
* Trim the > 1 value to .99999 for the model to fit

### Use all records

```{r}


model_data_long <- mutate(data_long, 
  p_all = ifelse(p_all >= 1, .99999, p_all)) %>%
  filter(!is.na(p_all)) %>%
  dplyr::select(time, tribe, p_all)

bezi_model <- gamlss(p_all ~ time, family = BEZI, data = model_data_long, trace = F)

summary(bezi_model)

```

```{r}

bezi_model <- tidy(bezi_model)

mean_t1 <- round(mean(filter(data_long, time == "time 1")$p_all, na.rm = T), 3)
mean_t2 <- round(mean(filter(data_long, time == "time 2")$p_all, na.rm = T), 3)
sd_t1 <- round(sd(filter(data_long, time == "time 1")$p_all, na.rm = T), 3)
sd_t2 <- round(sd(filter(data_long, time == "time 2")$p_all, na.rm = T), 3)

pvalue <- round(bezi_model[2,]$p.value, 3)
tvalue <- round(bezi_model[2,]$statistic, 3)
parameter <- bezi_model[2,]$parameter

```

**Interpretation**

* At the aggregate level,  the difference in proportion of protected area between time 1 (M = `r mean_t1`, SD = `r sd_t1`) and time 2 (M = `r mean_t2`, SD = `r sd_t2`) was statistically signficant (t(`r parameter`)= `r tvalue`, `r ifelse(pvalue < .001, "p < .001", paste0("p = ", pvalue))`).

### Use only records where tribes have time 1 and 2 data

```{r}

# Trim the > 1 value to .99999 for the model to fit
model_data_t1and2_long <- mutate(data_t1and2_long, 
  p_all = ifelse(p_all >= 1, .99999, p_all)) %>%
  filter(!is.na(p_all)) %>%
  dplyr::select(time, tribe, p_all)

bezi_model <- gamlss(p_all ~ time, family = BEZI, data = model_data_t1and2_long, trace = F)

summary(bezi_model)

```

```{r}

bezi_model <- tidy(bezi_model)

mean_t1 <- round(mean(filter(data_t1and2_long, time == "time 1")$p_all, na.rm = T), 3)
mean_t2 <- round(mean(filter(data_t1and2_long, time == "time 2")$p_all, na.rm = T), 3)
sd_t1 <- round(sd(filter(data_t1and2_long, time == "time 1")$p_all, na.rm = T), 3)
sd_t2 <- round(sd(filter(data_t1and2_long, time == "time 2")$p_all, na.rm = T), 3)

pvalue <- round(bezi_model[2,]$p.value, 3)
tvalue <- round(bezi_model[2,]$statistic, 3)
parameter <- bezi_model[2,]$parameter

```

**Interpretation**

* At the aggregate level for tribes with migration, the difference in proportion of protected area between time 1 (M = `r mean_t1`, SD = `r sd_t1`) and time 2 (M = `r mean_t2`, SD = `r sd_t2`) was statistically signficant (t(`r parameter`)= `r tvalue`, `r ifelse(pvalue < .001, "p < .001", paste0("p = ", pvalue))`).


### (2) Test for significant difference at tribe level

```{r, message = FALSE, warning = FALSE}


# tribe_with_dif_p_all <- filter(merged_data_tribe, avg_p_all_change_score > 0.01) %>% dplyr::select(tribe)

tribe_with_dif_p_all <- model_data_t1and2_long %>% group_by(tribe) %>% summarize(p = sum(p_all, na.rm = T)) %>% filter(p > 0)

no_test <- nrow(tribe_with_dif_p_all)

```

This can only be tested with the `r nrow(tribes_time1and2_lst)` tribes where migrations occured. Furthermore, only tribes where proportion of protected area have changed between time points and with more than one data point at each time point can their differences be tested for statistical significance. This reduce the number of tribes from `r nrow(tribes_time1and2_lst)` to `r no_test`.

### Run Zero-Inflated Beta Regression in Batch

* Run Zero-Inflated Beta Regression in batch using group_by and do at the tribe level.
* Include a try call to catch error.
* Use tidy from broom package to format the results into a data.frame.
* Replace NA estimate with all NA for that comparison.

```{r, message = FALSE, warning = FALSE}

model_data_t1and2_long <- filter(model_data_t1and2_long, tribe %in% tribe_with_dif_p_all$tribe)

model <- group_by(model_data_t1and2_long, tribe) %>%
do(tryCatch( {tidy(gamlss(p_all ~ time, family = BEZI, data =., trace = F))},
  error = function(e) {tidy((gamlss(p_all ~ time, family = BEZI, data =., trace = F)))}
    ))

model[!!rowSums(is.na(model)),-1] <- NA

model <- filter(model, parameter == "mu", term == "timetime 2")

```

Calculate number of test based only on tribes where there is non-zero difference and sufficient data point in proportion of protected area between time 1 and 2.

```{r}

no_test <- nrow(filter(model, !is.na(p.value)))

```

* Create sig column to flag statistical significance results. 
* p-value cutoff is adjusted to control for Type I error due to multiple comparisons using Bonferroni correction (p value threshold = .05 / number of tests or `r no_test`), adjusted p-value threshold = `r .5/no_test`.

```{r, message = FALSE, warning = FALSE}

model <- model %>%
  mutate(sig = ifelse(p.value < .05 / no_test, "yes", "no"))

```

* Add average proportion of protected area, distance, and no of unique FIPS to help with interpretation
* Rename some variables for prettier column headers

```{r}

results_df <- inner_join(model, merged_data_tribe, by = "tribe") %>%
  mutate(`Avg Diff Protected Area` = avg_p_all_t2 - avg_p_all_t1) %>%
  dplyr::select(tribe, sig, p.value, `Avg Diff Protected Area`, avg_p_all_t1, avg_p_all_t2, n_unique_FIPS_t1, n_unique_FIPS_t2, mid_dist) %>%
  arrange(p.value) %>%
  rename(
    `Avg Protected Area T1` = avg_p_all_t1,
    `Avg Protected Area T2` = avg_p_all_t2,
    `Unique FIPS T1` = n_unique_FIPS_t1,
    `Unique FIPS T2` = n_unique_FIPS_t2,
    `Mid Distance` = mid_dist)

```


### Results Table 
#### Ordered by p value in ascending order

```{r}

datatable(results_df,
          filter = "top",
          options = list(pageLength = 20)) %>%
   formatRound(columns = c('p.value'), digits = 3) %>%
   formatRound(columns = c('Avg Diff Protected Area', 'Avg Protected Area T1', 'Avg Protected Area T2', 'Mid Distance'), digits = 5)

```

```{r}

b_sig_tribe_lst <- filter(results_df, sig == "yes") %>%
  dplyr::select(tribe)
sig_tribe_lst <- filter(results_df, p.value < .05) %>%
  dplyr::select(tribe)

```

**Interpretation**

* The mean proportion of protected area comparisons for `r nrow(b_sig_tribe_lst)` tribes (`r b_sig_tribe_lst$tribe`) achieve statistical significance when the Bonferroni correction is used.
* The tests have low statistical power to detect differences given the number of observations at time 2 is much smaller than time 1.
* If Bonferroni correction is not used, proportion of protected area was significantly differ between time 1 and 2 for `r nrow(sig_tribe_lst)` tribes :(`r sig_tribe_lst$tribe`).
* Results with NA p values are from tribes where there isn't sufficient data points in both time point to perform the planned statistical tests.

**Overall Interpretation**

* Overall, a statistically significant difference was found at the aggregate level when data for all tribes were analyzed. The difference however was not statistically significant when only tribes with migrations were analyzed. At the tribe level, when correction for multiple comparisons was made, proportion of protected area for `r nrow(b_sig_tribe_lst)` tribes were found to be statistically differ between time 1 and time 2. 

* The lack of significant differences at the tribe level could be attributed to the low statistical power arises from the small number of observations at time 2. In some cases, there is only 1 data point in time 2 or time 1, which preclude the use of Welch's t-test to test for their mean differences.