---
title: "Explore Difference in Duration of Days with Hazards"
date: '2019-04-19'
output: html_document
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)

```

## Setup Library
Install these packages if neccessary.
```{r project_setup, message = FALSE, warning = FALSE}

library(readr)
library(gamlss)
library(tidyr)
library(knitr)
library(DT)
library(dplyr)
library(stringr)
library(scales)
library(broom)
library(ggplot2)
library(ggbeeswarm)
library(MASS)
library(pscl)
library(boot)
library(nlme)
library(cplm)

```

## Data Preparation

### Load Data
Load the data imported, processed and saved from "data wrangle change score centroid and map data.R".
```{r}

load('~/Dropbox/__Papers_in_Progress/_Indian_Removal/_Data_and_R/x_Github/tribal_lands/R_Analysis/processed_data.RData')

```

### Prepare Data

Keep distinct records within each time point only because keeping all pairwise records will inflate the number of observations in time 1 and 2.
```{r}

data_long <- distinct(merged_data_record_all_long, tribe, time, FIPS, .keep_all = TRUE)

```

Create data.frame to include only tribes with time 1 and 2 data.
```{r}

data_t1and2_long <- filter(data_long, tribe %in% tribes_time1and2_lst$tribe)

```

Convert time and tribe to factor for statistical modeling
```{r}

data_long <- data_long %>%
  ungroup() %>%
  mutate(tribe = factor(tribe),
         time = factor(time))

data_t1and2_long <- data_t1and2_long %>%
  ungroup() %>%
  mutate(tribe = factor(tribe),
         time = factor(time))

```


**Check Data**

First, confirm the data is correct, each tribe should have 2 summarized records in total, one for time 1 and one for time 2, so the resulted data.frame should has 0 row.
```{r}
t1and2_lst <- group_by(data_t1and2_long, tribe, time) %>% 
  count() %>%
  ungroup() %>%
  group_by(tribe) %>%
  count() %>%
  filter(n < 2)

nrow(t1and2_lst)
```


## Exploratory Analyses

### All Tribes, including those with time 1 or time 2 data only

### Plot Duration of Days with Hazards by Time

* The distribution of duration of days with hazards in time 1 and time 2 is skewed to the right and with outliers.
* The distirbution of duration of days with hazards is in general higher in time 1 compared to time 2.

```{r, message = FALSE, warning = FALSE, echo = FALSE}

ggplot(data_long, aes(shel_dura, fill = time)) +
  facet_grid(rows = vars(time), scales = "free") +
  geom_histogram(position = "dodge", bin = 70) +
  theme_minimal()

ggplot(data_long, aes(time, shel_dura, colour = time)) +
  geom_boxplot() +
  geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
  theme_minimal()

```

#### Look at those with duration of days with hazards only and 97.5th percentile cutoff

* The distirbution of duration of days with hazards is in general higher in time 1 compared to time 2 for tribes in counties with duration of days with hazards only.

```{r, message = FALSE, warning = FALSE}

data_long_shel_dura_only <- filter(data_long, shel_dura > 0)

ggplot(data_long_shel_dura_only, aes(shel_dura, fill = time)) +
  facet_grid(rows = vars(time), scales = "free") +
  geom_histogram(position = "dodge") +
  theme_minimal() +
  xlim(0, quantile(data_long_shel_dura_only$shel_dura, c(.975), na.rm = TRUE))  

ggplot(data_long_shel_dura_only, aes(time, shel_dura, colour = time)) +
  geom_boxplot() +
  geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
  theme_minimal() +
  ylim(0, quantile(data_long_shel_dura_only$shel_dura, c(.975), na.rm = TRUE))

```

### Tribes with both time 1 or time 2 data

### Plot Duration of Days with Hazards by Time

* The distribution of duration of days with hazards in time 1 and time 2 is skewed to the right and with outliers.
* The distirbution of duration of days with hazards is in general higher in time 1 compared to time 2.

```{r, message = FALSE, warning = FALSE}

ggplot(data_t1and2_long, aes(shel_dura, fill = time)) +
  facet_grid(rows = vars(time), scales = "free") +
  geom_histogram(position = "dodge", bin = 70) +
  theme_minimal()

ggplot(data_t1and2_long, aes(time, shel_dura, colour = time)) +
  geom_boxplot() +
  geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
  theme_minimal()

```

#### Look at only those with duration of days with hazards only and 97.5th percentile cutoff

* The distirbution of duration of days with hazards is in general higher in time 1 compared to time 2 for tribes in counties with duration of days with hazards only.

```{r, message = FALSE, warning = FALSE}

data_t1and2_long_shel_dura_only <- filter(data_t1and2_long, shel_dura > 0)

ggplot(data_t1and2_long_shel_dura_only, aes(shel_dura, fill = time)) +
  facet_grid(rows = vars(time), scales = "free") +
  geom_histogram(position = "dodge") +
  theme_minimal() +
  xlim(0, quantile(data_t1and2_long_shel_dura_only$shel_dura, c(.975), na.rm = TRUE))
  
ggplot(data_t1and2_long_shel_dura_only, aes(time, shel_dura, colour = time)) +
  geom_boxplot() +
  geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
  theme_minimal() +
  ylim(0, quantile(data_t1and2_long_shel_dura_only$shel_dura, c(.975), na.rm = TRUE))

```


### Plot relationship between Time 1 and Time 2 Duration of Days with Hazards at tribe level

* Compute the mean and median values of each tribe at time 1 and time 2. Look at the median as well as the mean because the median is a robust measure of central tendency and extreme-value resistent while the mean is heavily influenced by outliers. 

```{r, include = FALSE, echo = FALSE}

# Function to add R-squared number to scatterplot
lm_eqn = function(m) {

  l <- list(a = format(coef(m)[1], digits = 2),
      b = format(abs(coef(m)[2]), digits = 2),
      r2 = format(summary(m)$r.squared, digits = 3));

  if (coef(m)[2] >= 0)  {
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(R)^2~"="~r2,l)
  } else {
    eq <- substitute(italic(y) == a - b %.% italic(x)*","~~italic(R)^2~"="~r2,l)    
  }

  as.character(as.expression(eq));                 
}

```

#### Relationship between Time 1 and Time 2 Duration of Days with Hazards

* We found a large positive linear relationships between time 1 and time 2 duration of days with hazards using the mean (r = `r round(cor(merged_data_tribe$avg_shel_dura_t1, merged_data_tribe$avg_shel_dura_t2, use = "complete.obs"), 4)`) and the median (r = `r round(cor(merged_data_tribe$median_shel_dura_t1, merged_data_tribe$median_shel_dura_t2, use = "complete.obs"), 4)`)

```{r, message = FALSE, warning = FALSE, echo = FALSE}

ggplot(merged_data_tribe, aes(avg_shel_dura_t1, avg_shel_dura_t2)) +
  geom_point() +
  geom_smooth(method = 'lm',formula = y ~ x) +
  theme_minimal() +
  geom_text(aes(x = 2, y = 7, label = invisible(lm_eqn(lm(avg_shel_dura_t1 ~ avg_shel_dura_t2, merged_data_tribe)))), parse = TRUE)

ggplot(merged_data_tribe, aes(median_shel_dura_t1, median_shel_dura_t2)) +
  geom_point() +
  geom_smooth(method = 'lm',formula = y ~ x) +
  theme_minimal() +
  geom_text(aes(x = 1.9, y = 7.5, label = invisible(lm_eqn(lm(median_shel_dura_t1 ~ median_shel_dura_t2, merged_data_tribe)))), parse = TRUE)

```


## Test for Significant Difference

### (1) Test for significant difference at the aggregate level

* We applied three statistical models - Linear Mixed Model, Repeated Measure ANOVA, and Negative Binomial Model - to examine statistical significant difference between Time 1 and Time 2 duration of days with hazards.
* The models, as applicable, are run using all records from all tribes and tribes with both time 1 and 2 data.
* The model interpretation is based on the Negative Binomial Model, as this is the test most appropriate for the outcome. The Linear Mixed Model and Repeated Measure ANOVA results are shown for reference purposes.

### Use all records

Filter out NA outcomes
```{r}

model_data_long <- filter(data_long, !is.na(shel_dura))
model_data_t1and2_long <- filter(data_t1and2_long, !is.na(shel_dura))

```

### Linear Mixed Model

* Linear mixed model is a parametric test for comparing data when one or more of the independent variables should be model as a random effect because of variations by that variable.

```{r}

# Linear Mixed Model
lme_model <- nlme::lme(shel_dura ~ time, data = model_data_long, random = ~1|tribe)

summary(lme_model)

anova(lme_model)

```

### Repeated Measure ANOVA

* See Analysis below: Repeated Measure ANOVA can only be run with tribes with both time 1 and time 2 data.

### Negative Binomial Regression Model

* Negative binomial regression is a parameteric test for modeling count variables such as duration of days with hazards and is usually for over-dispersed count outcome variables. Unlike t-test or ANOVA, this test is appropriate for data that has a non-normally distribute positive count or value, such as the outcome duration of days with hazards.

```{r, warning = FALSE, error = FALSE, message = FALSE}

# Negative Binomial Model
nb_model <- glm.nb(shel_dura ~ time, data = model_data_long)

nb_model_summary <- summary(nb_model)

summary(nb_model)

```

```{r}

model_para <- coef(nb_model_summary)

mean_t1 <- round(mean(filter(data_long, time == "time 1")$shel_dura, na.rm = T), 3)
mean_t2 <- round(mean(filter(data_long, time == "time 2")$shel_dura, na.rm = T), 3)
sd_t1 <- round(sd(filter(data_long, time == "time 1")$shel_dura, na.rm = T), 3)
sd_t2 <- round(sd(filter(data_long, time == "time 2")$shel_dura, na.rm = T), 3)

pvalue <- round(model_para[2,4], 3)
zvalue <- round(model_para[2,3], 3)
parameter <- NA

```

**Interpretation**

* At the aggregate level,  the difference in duration of days with hazards between time 1 (M = `r mean_t1`, SD = `r sd_t1`) and time 2 (M = `r mean_t2`, SD = `r sd_t2`) was statistically signficant (z = `r zvalue`, `r ifelse(pvalue < .001, "p < .001", paste0("p = ", pvalue))`).


### Use only records where tribes have time 1 and 2 data

### Linear Mixed Model

```{r}

# Linear Mixed Model
lme_model <- nlme::lme(shel_dura ~ time, data = model_data_t1and2_long, random = ~1|tribe)

summary(lme_model)

anova(lme_model)

```

### Repeated Measure ANOVA

* Repeated Measure ANOVA can only be run with tribes with both time 1 and time 2 data.

```{r}

# Repeated Measure ANOVA
aov_model <- aov(shel_dura ~ time + Error(tribe / time), data = model_data_t1and2_long)

summary(aov_model)

```

### Negative Binomial Regression Model

* Negative binomial regression is a parameteric test for modeling count variables such as duration of days with hazards and is usually for over-dispersed count outcome variables. Unlike t-test or ANOVA, this test is appropriate for data that has a non-normally distribute positive count or value, such as the outcome duration of days with hazards.

```{r, warning = FALSE, error = FALSE, message = FALSE}

# Negative Binomial Model
nb_model <- glm.nb(shel_dura ~ time, data = model_data_t1and2_long)

nb_model_summary <- summary(nb_model)

summary(nb_model)

```

```{r}

model_para <- coef(nb_model_summary)

mean_t1 <- round(mean(filter(data_t1and2_long, time == "time 1")$shel_dura, na.rm = T), 3)
mean_t2 <- round(mean(filter(data_t1and2_long, time == "time 2")$shel_dura, na.rm = T), 3)
sd_t1 <- round(sd(filter(data_t1and2_long, time == "time 1")$shel_dura, na.rm = T), 3)
sd_t2 <- round(sd(filter(data_t1and2_long, time == "time 2")$shel_dura, na.rm = T), 3)

pvalue <- round(model_para[2,4], 3)
zvalue <- round(model_para[2,3], 3)
parameter <- NA

```

**Interpretation**

* At the aggregate level for tribes with migration, the difference in duration of days with hazards area between time 1 (M = `r mean_t1`, SD = `r sd_t1`) and time 2 (M = `r mean_t2`, SD = `r sd_t2`) was not statistically signficant (z = `r zvalue`, `r ifelse(pvalue < .001, "p < .001", paste0("p = ", pvalue))`).


### (2) Test for significant difference at tribe level

* At the tribe level, only the Negative Binomial Model is run.

```{r, message = FALSE, warning = FALSE}

tribe_with_dif <- filter(merged_data_tribe, avg_shel_dura_change_score > 0) %>% group_by(tribe) %>% count()

no_test <- nrow(tribe_with_dif)

```

This can only be tested with the `r nrow(tribes_time1and2_lst)` tribes where migrations occured. Furthermore, only tribes where duration of days with hazards have changed between time points and with more than one data point at each time point can their differences be tested for statistical significance. This reduce the number of tribes from `r nrow(tribes_time1and2_lst)` to `r no_test`.

### Run Negative Binomial Regression in Batch

* Run Negative Binomial Regression Model in batch using group_by and do at the tribe level.
* Include a try call to catch error.
* Format the results into a data.frame.
* Replace NA estimate with all NA for that comparison.

```{r, message = FALSE, warning = FALSE, echo = FALSE}

model <- group_by(model_data_t1and2_long, tribe) %>%
do(tryCatch(
  {tidy(glm.nb(shel_dura ~ time, data = .))},
    error = function(e) {data.frame(Estimate = NA)}
))

model <- filter(model, term == "timetime 2")

```

Calculate number of test based only on tribes where there is non-zero difference and sufficient data point in duration of days with hazards between time 1 and 2.

```{r}

no_test <- nrow(filter(model, !is.na(p.value)))

```

* Create sig column to flag statistical significance results. 
* p-value cutoff is adjusted to control for Type I error due to multiple comparisons using Bonferroni correction (p value threshold = .05 / number of tests or `r no_test`), adjusted p-value threshold = `r .5/no_test`.

```{r, message = FALSE, warning = FALSE}

model <- model %>%
  mutate(sig = ifelse(p.value < .05 / no_test, "yes", "no"))

```

* Add days duration, distance, and no of unique FIPS to help with interpretation
* Rename some variables for prettier column headers

```{r}

results_df <- inner_join(model, merged_data_tribe, by = "tribe") %>%
  mutate(`Avg Diff Days Dura` = avg_shel_dura_t2 - avg_shel_dura_t1) %>%
  dplyr::select(tribe, sig, p.value, `Avg Diff Days Dura`, avg_shel_dura_t1, avg_shel_dura_t2, n_unique_FIPS_t1, n_unique_FIPS_t2, mid_dist) %>%
  arrange(p.value) %>%
  rename(
    `Avg Days Dura T1` = avg_shel_dura_t1,
    `Avg Days Dura T2` = avg_shel_dura_t2,
    `Unique FIPS T1` = n_unique_FIPS_t1,
    `Unique FIPS T2` = n_unique_FIPS_t2,
    `Mid Distance` = mid_dist)

```


### Results Table 
#### Ordered by p value in ascending order

```{r}

datatable(results_df,
          filter = "top",
          options = list(pageLength = 20)) %>%
   formatRound(columns = c('p.value'), digits = 3) %>%
   formatRound(columns = c('Avg Diff Days Dura', 'Avg Days Dura T1', 'Avg Days Dura T2', 'Mid Distance'), digits = 5)

```

```{r}

b_sig_tribe_lst <- filter(results_df, sig == "yes") %>%
  dplyr::select(tribe)
sig_tribe_lst <- filter(results_df, p.value < .05) %>%
  dplyr::select(tribe)

```

**Interpretation**

* The mean duration of days with hazards comparisons for `r nrow(b_sig_tribe_lst)` tribes (`r b_sig_tribe_lst$tribe`) achieve statistical significance when the Bonferroni correction is used.
* The tests have low statistical power to detect differences given the number of observations at time 2 is much smaller than time 1.
* If Bonferroni correction is not used, duration of days with hazards was significantly differ between time 1 and 2 for `r nrow(sig_tribe_lst)` tribes :(`r sig_tribe_lst$tribe`).
* Results with NA p values are from tribes where there isn't sufficient data points in both time point to perform the planned statistical tests.

**Overall Interpretation**

* Overall, statistically significant difference were found at the aggregate level when data for all tribes and but not when tribes with migrations were analyzed on the outcome duration of days with hazards,

* At the tribe level, when correction for multiple comparisons was made, duration of days with hazards for `r nrow(b_sig_tribe_lst)` tribes were found to be statistically differ between time 1 and time 2. 

* The lack of significant differences at the tribe level could be attributed to the low statistical power arises from the small number of observations at time 2. In some cases, there is only 1 data point in time 2 or time 1.