---
title: "Appendix: Results"
author: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
header-includes:
   - \usepackage{rotating, graphicx}
output: bookdown::pdf_document2
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)

```

```{r project_setup, message = FALSE, warning = FALSE, include=FALSE}

library(readr)
library(gamlss)
library(tidyr)
library(knitr)
library(DT)
library(dplyr)
library(purrr)
library(stringr)
library(scales)
library(broom)
library(ggplot2)
library(ggbeeswarm)
library(MASS)
library(pscl)
library(boot)
library(nlme)
library(cplm)
library(conflicted)
library(fixest)
library(sjPlot)
library(stargazer)
library(texreg)
library(clubSandwich)
library(srvyr)
library(survey)

conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")

load("../final_data.Rdata")

source("support_functions2.R")



#Constructing datasets
data_long <- distinct(merged_data_record_all_long, tribe, time, FIPS, .keep_all = TRUE) %>%
  ungroup() %>%
  mutate(tribe = factor(tribe),
         time = factor(time),
         oil_avg = oil_avg/1000,
         gas_avg = gas_avg/1000) 

data_t1and2_long <- filter(data_long, tribe %in% tribes_time1and2_lst$tribe)

#Constructing weights and survey objects
data_long <- data_long %>%
  group_by(tribe,time) %>%
  summarise(wgt=1/n()) %>%
  ungroup() %>%
  left_join(data_long,
            .,
            by=c("tribe","time"))

svy_data_long <- data_long %>% 
  as_survey_design(ids = tribe,probs = wgt)

data_t1and2_long <- data_t1and2_long %>%
  group_by(tribe,time) %>%
  summarise(wgt=1/n()) %>%
  ungroup() %>%
  left_join(data_t1and2_long,
            .,
            by=c("tribe","time"))
  
svy_data_t1and2_long <- data_t1and2_long %>% 
  as_survey_design(ids = tribe,probs = wgt)
```

\newpage

# Introduction

The objective of this supplement is to provide detail on the analysis of County Equivalent (CCE) characteristics in the historical and present-day time periods.  We begin by describing the data used to assess the differences in CCE characteristics across lands in the two time periods.  We then detail the methods used to compare the CCEs across time along a suite of characteristics: climate, mineral access, and proximity to federal lands.  Finally, we present the results of our analyses as well as assess the robustness of the results.



# Data Descriptions

We focus on land characteristics that are either durable over long time periods or not heavily impacted by the human inhabitants of the land.  We divide the characteristics into categories: climate, mineral resource access, and national lands. The set of climate characteristics consist of number of extreme temperature days, drought, precipitation, and a measure of wildfire hazard potential.  The set of mineral resource access characteristics include access to oil and gas basins, oild and gas production, and number of wells.  Finally, we assess the proximity of historical and present-day CCEs to federal lands.  The following sections describe the data sources and any processing to construct the variables for analysis.



Table \ref{tab:sum_full} contains summary statistics for the dataset used in the analyses.  However, there are many instances where a tribe is present in only the present-day set or the historical set.  We also present the summary statistics of a dataset with only tribes present in both periods.  Table \ref{tab:sum_full} contains the summary statistics of the Present-day and Historical dataset.  While the number of observations is clearly smaller in the dataset with tribes present in both periods, the distribution of the datasets is very similar suggesting that these tribes who enter or exit the dataset are not systematically different from those in both periods with regard to our CCE characteristics.



## Heat
The National Weather Service's Heat Index incorporates both relative humidity and actual air temperature to describe how hot the temperature feels in degrees Farenheit. We utilize a measure of the number of days per year that the Heat Index is greater than 100 degrees Farenheit.
Dates: CAN'T FIND ACTUAL DATA DOWNLOAD SITE, SO CAN'T FIND DATES.

National Weather Service, Heat Index, (available at https://www.weather.gov/safety/heat-index).

## Drought
We measure drought conditions as the Palmer Drought Severity Index (PDSI). The PDSI is a unitless measure which assesses exposure to drought and ranges from -10 (extreme drought) to +10 (extreme wet). We gather weekly PDSI measures gridded (4km resolution) across the continental US from gridMET (Abatzoglou, 2013).  First, we construct CCE weekly PDSI averages using GIS to spatially intersect CCE boundaries with gridded weather.  Second, we calculate weekly decadal averages.  We construct the variable *Drought* by taking the difference between the 2010 and 1980 decadal averages for each CCE in the continental US. This variable captures the long-term climate impacts on CCEs.
 
## Precipitation
Oregon State University's PRISM Climate Group calcualtes average precipitation (inches) over 30-year time periods. The data that we use is calculated between 1981 and 2010.

PRISM Climate Group, Northwest Alliance for Computational Science and Engineering, PRISM Climate Data, (available at http://prism.oregonstate.edu/).

## Wildfire Hazard Potential
A changing climate is expected to alter wildfire behavior in the US, and particularly in the Western US (Abazoglou and Williams, 2016; Westerling et al. 2006).  We construct a measure of wildfire risk using a gridded (270 meter) index called Wildfire Hazard Potential (WHP) (Dillon, 2018).  The WHP is a discrete scale from 1 (very low fire hazard potential) to 5 (very high hazard potential). We calculate the mean WHP of all grid cells within the county boundary.


Abatzoglou, J. T. (2013). Development of gridded surface meteorological data for ecological applications and modelling. International Journal of Climatology, 33(1), 121–131. https://doi.org/10.1002/joc.3413

Abatzoglou, J. T., & Williams, A. P. (2016). Impact of anthropogenic climate change on wildfire across western US forests. Proceedings of the National Academy of Sciences, 113(42), 11770–11775. https://doi.org/10.1073/pnas.1607171113

Dillon, Gregory K. 2018. Wildfire Hazard Potential (WHP) for the conterminous United States (270-m GRID), version 2018 classified. 2nd Edition. Fort Collins, CO: Forest Service Research Data Archive. https://doi.org/10.2737/RDS-2015-0046-2

Westerling, A. L., Hidalgo, H. G., Cayan, D. R., & Swetnam, T. W. (2006). Warming and Earlier Spring Increase Western U.S. Forest Wildfire Activity. Science, 313(5789), 940–943. https://doi.org/10.1126/science.1128834

## Oil and Gas Basins
The U.S. Energy Information Administration provides a map of sedimentary basin boundaries within the continental United States. Using this map, we construct a binary variable which describes whether a CCE does or does not overlap an oil or gas basin.

Oil and Gas Exploration, Resources, and Production. U.S. Energy Information Administration, (available at https://www.eia.gov/maps/maps.htm).

## Oil and Gas Production
The U.S. Department of Agriculture reports gross withdrawls of oil and gas at the county level between 2000 and 2011.

WHAT UNITS?
NEED CITATION. IS IT THIS? https://data.nal.usda.gov/dataset/county-level-oil-and-gas-production-us

## Oil and Gas Wells
The U.S. Geological Survey reports all known well locations across the continental United States between 1859 and 2005. We calculate the total number of wells drilled in each CCE over this 146-year period.

NEED CITATION, JUSTIN RECEIVED DIRECTLY FROM USGS

## Federal Lands
The U.S. Geological Survey's Protected Lands Database of the U.S. (PAD-US) is a spatial inventory of all formally protected lands. We select only lands protected by the Federal Government (e.g. national parks, national forests, etc.). We calculate total land area of a CCE which is designated as a federally protected area.

CONFIRM WE ONLY USE FEDERAL LANDS
WHAT UNIT (ACRES? BEN DID THIS)

ProtectedLands.net. A Resource for the Protected Areas Database of the United States (PAD-US), (available at http://www.protectedlands.net).


```{r, message = FALSE, warning = FALSE, echo = FALSE, results='asis'}

for_summary <- vector("list",2)

for_summary[[1]] <- data_long %>% 
  select(`Number of CCEs`=n_unique_FIPS,
         `Days over 100F`=h_100_hist,
         `Drought`=drt_median,
         `Precipitation`=precip,
         `Wildfire Hazard Potential`=fire_mean,
         `Oil and Gas Basin`=og_basin,
         `Oil Production`=oil_avg,
         `Gas Production`=gas_avg,
         `Well Count`=og_well_count,
         `Fraction Federal Land`=p_all) %>%
  as.data.frame()

for_summary[[2]] <- data_t1and2_long %>% 
  select(`Number of CCEs`=n_unique_FIPS,
         `Days over 100F`=h_100_hist,
         `Drought`=drt_median,
         `Precipitation`=precip,
         `Wildfire Hazard Potential`=fire_mean,
         `Oil and Gas Basin`=og_basin,
         `Oil Production`=oil_avg,
         `Gas Production`=gas_avg,
         `Well Count`=og_well_count,
         `Fraction Federal Land`=p_all) %>%
  as.data.frame()


stargazer(for_summary[[1]],
          digits = 2,
          title = "Full Dataset",
          header = F,
          label = "tab:sum_full")

stargazer(for_summary[[2]],
          digits = 2,
          title = "Present-day and Historical Dataset",
          header = F,
          label = "tab:sum_both")



```




# Methods

We employ several statistical methods to test whether characteristics of the historical lands differ from the present-day lands.  Our primary method to compare the historical and present-day CCEs is a linear regression of the CCE characteristic as a function of a binary indicator for present-day lands (and an intercept), which amounts to simple ANOVA test of whether the means are equal in the historical and present-day CCEs.  The intercept in these models is the mean of the CCE characteristic in the historial period while the present-day coefficient represents the change from the historical to the present-day period.  All statistical tests are conducted using cluster-robust standard errors, which account for heteroskedasticity and serial correlation that may exist within a tribe due to the proximity of CCEs within a tribe's historical or present-day extent.

We assess the robustness of our estimate using several alternative model specifications and two forms of the data: 1) only tribes with records in the present-day and historical period, and 2) all tribes including those with records in only one time period (denoted Full in the following tables).  In each table below, we present a set of the following models:

- OLS: Ordinary Least Squares (OLS) model using only data on tribes with records in the historical and present-day periods.  

- Weighted OLS: weighted OLS model using only data on tribes with records in the historical and present-day periods.  We construct weights as the inverse of the total number of CCEs associated with a tribe in each time period.  The weighted regression model effectively places equal weight on each tribe given that the number of CCEs varies with the historical range of the tribe.  Larger, more dominant, or tribes with CCEs in the Eastern US may include more CCEs, which effectively increases the weight on those tribes in a simple regression setting. By weighting the observations, the results can be interpretted as a tribal-level analysis. 

- Full OLS: OLS model using the full dataset, which includes tribes present in either the historical or present-day periods. The full dataset increases the sample size but may introduce bias due to the dissolution and formation of tribes between our time periods.  

- Full Weighted OLS: weighted OLS model using the full dataset.  

- Poisson: a Poisson regression when the data are integer count data.

- Tribe FE: an OLS regression with tribe fixed effects.  The fixed effect regression estimates tribe-specific means in the historical period, but a common coefficient on the difference between the historical and present-day periods.  This model would control for unobserved factors within a tribe that may influence any relocation policy and thus the characteristics of the CCEs in both the historical and present-day periods.  

- BEZI: zero-inflated Beta regression when the dependent variable is bounded between zero and one (e.g., percent).


# Results

This section presents the results of the analysis along with several robustness checks.

## CCEs Inhabited

We compare the spatial extent of tribe's historical and present-day areas as measured by the number of CCEs.  We estimate the difference between the number of CCEs reported as historical lands and the number of CCEs reported as present-day lands using several regression models to assess the robustness of the relationship. 


```{r, message = FALSE, warning = FALSE, echo = FALSE, results='asis'}
model.shell <- vector("list",5)
dep.var <- "n_unique_FIPS"

model.shell[[1]] <- ols_clustered(dep.var,df=data_t1and2_long)
model.shell[[2]] <- ols_weighted(dep.var,df=svy_data_t1and2_long)
model.shell[[3]] <- ols_clustered(dep.var,df=data_long)
model.shell[[4]] <- ols_weighted(dep.var,df=svy_data_long)
model.shell[[5]] <- glm_clustered(dep.var,df=data_t1and2_long,family = "poisson")

sg_table(model.shell,
         dep.name = "Number of CCEs",
         column.labels = c("OLS","Weighted OLS","Full OLS","Full Weighted OLS","Poisson"),
         label = "tab:cce",
         title = "Extent of Area Occupied")
```

The results in Table \ref{tab:cce} indicate that tribes occupied far fewer CCEs in the present period relative to the historical period.  The results in column 1 suggest that tribes occupied an average of 146.7 CCEs during the historical period. By the present day, the average number of CCEs fell by 136.303 (a `r percent(1-(model.shell[[1]]$results[1,1]+model.shell[[1]]$results[2,1])/model.shell[[1]]$results[1,1])` reduction).  The relationship is robust to all specifications.  However, the results of column 2 (weighted OLS) indicate that the abolute estimated effect is heavily influenced by large tribes, yet the percentage reduction in CCEs is of similar magnitude (`r percent(1-(model.shell[[2]]$results[1,1]+model.shell[[2]]$results[2,1])/model.shell[[2]]$results[1,1])`). 




## Heat

We begin with the heat index, which represents the number of days per year that a CCE exceeded 100 degrees F. The results in Table \ref{tab:heat} suggest that the present-day lands experience 2-3 more days in excess of 100 degrees per year compared to historical lands, and that this relationship is fairly robust across specifications. The point estimates range from 2.52 (Weighted OLS) to 2.92 (Full OLS).  The coefficients of the Poisson model are not directly comparable to the OLS estimates.  The model suggests that historical lands experience about 5.5 (5.5=exp(1.705)) days a year over 100 degrees, while the present-days lands experience 2.5 (2.5=exp(1.705)*(exp(.387)-1)) additional days over 100, which is comparable to the OLS estimates.

```{r, message = FALSE, warning = FALSE, echo = FALSE, results='asis'}
model.shell <- vector("list",5)
dep.var <- "h_100_hist"

model.shell[[1]] <- ols_clustered(dep.var,df=data_t1and2_long)
model.shell[[2]] <- ols_weighted(dep.var,df=svy_data_t1and2_long)
model.shell[[3]] <- ols_clustered(dep.var,df=data_long)
model.shell[[4]] <- ols_weighted(dep.var,df=svy_data_long)
model.shell[[5]] <- glm_clustered(dep.var,df=data_t1and2_long,family = "poisson")

sg_table(model.shell,
         dep.name = "Days per Year in excess of 100 degrees F",
         column.labels = c("OLS","Weighted OLS","Full OLS","Full Weighted OLS","Poisson"),
         label = "tab:heat",
         title = "Extreme Heat")
```




## Drought

We calculate the median Palmer Drought Severity Index (PDSI) of all grid cells within the county boundary for each week from 1980-2017.  We then calculate the  mean PDSI over all weeks 1980-2017.  

Table \ref{tab:drought} present the results. Our OLS, Weighted OLS, Full OLS, and Tribe Fixed Effects models all indicate that present-day lands are significantly drier than historical lands, with point estimates ranging between -0.06 (Weighted OLS) and -0.18 (OLS).  The Full Weighted OLS is the only model resulting in a significant and positive coefficient for Present-day Change (.08), indicating a decline in drought conditions over time. 

```{r, message = FALSE, warning = FALSE, echo = FALSE}

# ggplot(data_t1and2_long, aes(time, drt_median, colour = time)) +
#   geom_boxplot(varwidth = T) +
#   geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
#   scale_y_reverse(breaks = seq(-1.5,1,by=.5), labels = c("More Drought -1.5","-1.0","-0.5","0","0.5","Less Drought 1.0")) +
#   scale_colour_manual(values = c('#E0E022','#ff0000'),aesthetics = c("colour", "fill")) +
#   theme_minimal() +
#   xlab("") +
#   ylab("") +
#   scale_x_discrete(labels = c("time 1" = "Historical",
#                               "time 2" = "Present-day")) +
#   theme(legend.position = "none") 

```



```{r, message = FALSE, warning = FALSE, echo = FALSE, results='asis'}
model.shell <- vector("list",5)
dep.var <- "drt_median"

model.shell[[1]] <- ols_clustered(dep.var,df=data_t1and2_long)
model.shell[[2]] <- ols_weighted(dep.var,df=svy_data_t1and2_long)
model.shell[[3]] <- ols_clustered(dep.var,df=data_long)
model.shell[[4]] <- ols_weighted(dep.var,df=svy_data_long)
model.shell[[5]] <- feols_clustered(dep.var,df=data_t1and2_long)

sg_table(model.shell,
         dep.name = "Median PDSI",
         column.labels = c("OLS","Weighted OLS","Full OLS","Full Weighted OLS","Tribe FE"),
         label = "tab:drought",
         title = "Drought")
```


## Precipitation

We compare the mean annual precipitation (mm) in present-day and historical CCEs, utilizing climate data from the PRISM Climate Group. 

```{r, message = FALSE, warning = FALSE, echo = FALSE}


# ggplot(data_long, aes(time, precip, colour = time)) +
#   geom_boxplot() +
#   geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
#   theme_minimal()
# 
# 
# ggplot(data_t1and2_long, aes(time, precip, colour = time)) +
#   geom_boxplot() +
#   geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
#   theme_minimal()

```


We report that the difference between historical and present-day lands are statistically indistinguishable based on our primary specification (Table \ref{tab:precip}).  While the unweighted point estimates on present day are negative, the corresponding estimates on the weighted version .


```{r, message = FALSE, warning = FALSE, echo = FALSE, results='asis'}
model.shell <- vector("list",5)
dep.var <- "precip"

model.shell[[1]] <- ols_clustered(dep.var,df=data_t1and2_long)
model.shell[[2]] <- ols_weighted(dep.var,df=svy_data_t1and2_long)
model.shell[[3]] <- ols_clustered(dep.var,df=data_long)
model.shell[[4]] <- ols_weighted(dep.var,df=svy_data_long)
model.shell[[5]] <- feols_clustered(dep.var,df=data_t1and2_long)

sg_table(model.shell,
         dep.name = "Mean Annual Precipitation",
         column.labels = c("OLS","Weighted OLS","Full OLS","Full Weighted OLS","Tribe FE"),
         label = "tab:precip",
         title = "Precipitation")
```

While the evidence for a difference in precipitation across the present-day and historical CCEs is weak, the weighted OLS regressions indicate that the present-day lands experience slightly more precipitation.  This result suggests that there exists a large amount of variation across tribes, and that there are some tribes that occupied more CCEs that experienced less precipitation on some of the lands.


## Wildfire Hazard Potential



We compare mean Wildfire Hazard Potential (WHP) rating of all cells within a CCE boundary in the present-day and historical lands.  Figure 2b suggests that the present-day lands have a higher wildfire hazard potential.  Table S5 generally confirms that present-day lands have higher wildfire hazard potential compared to historical lands.

```{r, message = FALSE, warning = FALSE, echo = FALSE}


# ggplot(data_long, aes(time, fire_mean, colour = time)) +
#   geom_boxplot() +
#   geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
#   theme_minimal()
# 
# 
# ggplot(data_t1and2_long, aes(time, fire_mean, colour = time)) +
#   geom_boxplot() +
#   geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
#   scale_colour_manual(values = c('#32CD32','#ff0000'),aesthetics = c("colour", "fill")) +
#   theme_minimal() +
#   xlab("") +
#   ylab("") +
#   scale_x_discrete(labels = c("time 1" = "Historical",
#                               "time 2" = "Present-day")) +
#   theme(legend.position = "none") 
  

```
Figure caption: Wildfire hazard potential in historical and present-day CCEs.  While indigenous peoples were concentrated on fewer total CCEs (width of distribution), the mean WHP is higher in the present-day CCEs than the historical.

```{r, message = FALSE, warning = FALSE, echo = FALSE, results='asis'}
model.shell <- vector("list",5)
dep.var <- "fire_mean"

model.shell[[1]] <- ols_clustered(dep.var,df=data_t1and2_long)
model.shell[[2]] <- ols_weighted(dep.var,df=svy_data_t1and2_long)
model.shell[[3]] <- ols_clustered(dep.var,df=data_long)
model.shell[[4]] <- ols_weighted(dep.var,df=svy_data_long)
model.shell[[5]] <- feols_clustered(dep.var,df=data_t1and2_long)

sg_table(model.shell,
         dep.name = "Mean Wildfire Hazard Potential",
         column.labels = c("OLS","Weighted OLS","Full OLS","Full Weighted OLS","Tribe FE"),
         title = "Wildfire Hazard Potential")
```

Unweighted OLS models suggest that present-day area have higher wildfire hazard potential relative to historical lands.  However, the weighted models find no relationship (Weighted OLS) and even a slight negative relationship (Full Weighted OLS).  These results suggest that there are likely tribes that covered many CCEs that moved to lands with higher wildfire hazard potential.  While wildfire hazard potential is a function of the natural environment, it is also influenced by human modifications of the natural and built environment.  



## Oil and Gas Basins

We evaluate access to oil and gas based on the likelihood that a tribe's CCEs lie over subsurface oil and gas.  Our main specification, OLS, in Table S6 (column 1) indicates that present-day lands are less likely to have access to subsurface oil and gas.  Estimating OLS with a binary dependent variable is known as a linear probability model (LPM).  The LPM has two well-known shortcomings: 1) bias when the mass of the distribution lies outside of the unit interval, and 2) heteroskedasticity.  Since we estimate all models with robust standard errors, we should correct for heteroskedasticity.  We estimate a logistic regression (column 5) to assess the robustness of the difference between present-day and historical lands.  The results of the logistic regression indicate that present-day lands have less access to oil and gas supporting the results of our main specification.  However, the results of the weighted OLS (column 2) and the models using all data (columns 3 and 4) are less clear.  

```{r, message = FALSE, warning = FALSE, echo = FALSE, results='asis'}
model.shell <- vector("list",5)
dep.var <- "og_basin"

model.shell[[1]] <- ols_clustered(dep.var,df=data_t1and2_long)
model.shell[[2]] <- ols_weighted(dep.var,df=svy_data_t1and2_long)
model.shell[[3]] <- ols_clustered(dep.var,df=data_long)
model.shell[[4]] <- ols_weighted(dep.var,df=svy_data_long)
model.shell[[5]] <- glm_clustered(dep.var,df=data_t1and2_long,family = "binomial")

sg_table(model.shell,
         dep.name = "Presence of Subsurface Oil and Gas",
         column.labels = c("OLS","Weighted OLS","Full OLS","Full Weighted OLS","Logit"),
         title = "Oil and Gas Access")
```




## Oil

We compare oil production (measured in millions of barrels) between historical and present-day lands, with model specifications providing some evidence that there is less oil production on present-day CCE's. While our primary OLS specification shows an insignificant reduction in oil production (1.23 million barrels), additional model specifications show significant reductions (between 2.59 and 18.43 million barrels). 

The distributions are highly skewed. <- Jude made this note, I can't see distributions in the PDF so am leaving this here for now.

```{r, message = FALSE, warning = FALSE, echo = FALSE, results='asis'}
model.shell <- vector("list",5)
dep.var <- "oil_avg"

model.shell[[1]] <- ols_clustered(dep.var,df=data_t1and2_long)
model.shell[[2]] <- ols_weighted(dep.var,df=svy_data_t1and2_long)
model.shell[[3]] <- ols_clustered(dep.var,df=data_long)
model.shell[[4]] <- ols_weighted(dep.var,df=svy_data_long)
model.shell[[5]] <- feols_clustered(dep.var,df=data_t1and2_long)

sg_table(model.shell,
         dep.name = "Oil Production (millions of barrels)",
         column.labels = c("OLS","Weighted OLS","Full OLS","Full Weighted OLS","Tribe FE"),
         title = "Oil Production")
```

## Gas

Drawing on the U.S. Department of Agriculture's natural gas production data (measured in ?? cubic feet), we compare gas production between historical and present-day lands.  While our OLS model shows significantly greater (4.29 million cubic feet) gas production on present-day lands, the confidence interval is large and crosses zero.  Additional model specification yield mixed results. Our Full OLS model similarly shows a significant increase in production (5.2 million cubic feet), but the Weighted, Full Weighted OLS, and Tribe Fixed Effects models show insignificant changes in gas production between time periods. This variation suggests that our OLS findings are not especially robust, and that Tribes with larger CCE coverage tend to have higher natural gas production in the present-day, thus influencing unweighted model outcomes.


```{r, message = FALSE, warning = FALSE, echo = FALSE, results='asis'}
model.shell <- vector("list",5)
dep.var <- "gas_avg"

model.shell[[1]] <- ols_clustered(dep.var,df=data_t1and2_long)
model.shell[[2]] <- ols_weighted(dep.var,df=svy_data_t1and2_long)
model.shell[[3]] <- ols_clustered(dep.var,df=data_long)
model.shell[[4]] <- ols_weighted(dep.var,df=svy_data_long)
model.shell[[5]] <- feols_clustered(dep.var,df=data_t1and2_long)

sg_table(model.shell,
         dep.name = "Gas Production ??units",
         column.labels = c("OLS","Weighted OLS","Full OLS","Full Weighted OLS","Tribe FE"),
         title = "Gas Production")
```


## Oil and Gas Wells

Utilizing U.S. Geological Survey data on well locations between 1859 - 2005, we evaluate differences in the total number of oil and gas wells between historical and present-day lands. All model specifications indicate that the total number of wells is significantly higher on present-day lands, suggesting that this relationship is robust. Estimates of the average number of additional wells per present-day CCE range from 94.82 (OLS) to 141.38 (Full OLS) compared to historical CCE's.

```{r, message = FALSE, warning = FALSE, echo = FALSE, results='asis'}
model.shell <- vector("list",5)
dep.var <- "og_well_count"

model.shell[[1]] <- ols_clustered(dep.var,df=data_t1and2_long)
model.shell[[2]] <- ols_weighted(dep.var,df=svy_data_t1and2_long)
model.shell[[3]] <- ols_clustered(dep.var,df=data_long)
model.shell[[4]] <- ols_weighted(dep.var,df=svy_data_long)
model.shell[[5]] <- feols_clustered(dep.var,df=data_t1and2_long)

sg_table(model.shell,
         dep.name = "Count of Oil and Gas Wells",
         column.labels = c("OLS","Weighted OLS","Full OLS","Full Weighted OLS","Tribe FE"),
         title = "Oil and Gas Wells")
```


## Federal Lands

Finally, we study the difference between proximity to public lands during the historical and present-day periods.  We estimate two types of models on the two datasets.  The first model is a Zero-Inflated Beta model designed to analyze data bounded by 0 and 1. The zero-inflated version of the model accounts for the over abundance of zeros (Table \ref{tab:sum_both}).  The results suggest that present-day lands are closer to public lands compared to historical lands.  The BEZI and Full BEZI coefficient estimates on Present-day Change is 0.506 and 0.519, which implies that the odds of being in proximity to public lands in the present-day period are 1.65 higher than in the historial period.  The OLS estimates suggest that the present-day CCEs are about twice as likely to be near public lands.  This larger effect is likely due to the mispecification of the model of the limited dependent variable.   

```{r, message = FALSE, warning = FALSE, echo = FALSE, include=FALSE}

bezi_datat1t2 <- mutate(data_t1and2_long,
                    p_all = ifelse(p_all >= 1, .99999, p_all)) %>%
  filter(!is.na(p_all)) %>%
  dplyr::select(time, tribe, p_all,wgt)

bezi_data <- mutate(data_long,
                    p_all = ifelse(p_all >= 1, .99999, p_all)) %>%
  filter(!is.na(p_all)) %>%
  dplyr::select(time, tribe, p_all,wgt)

bezi_modelt1t2 <- gamlss(p_all ~ time, family = BEZI, data = bezi_datat1t2, trace = F)
bezi_model <- gamlss(p_all ~ time, family = BEZI, data = bezi_data, trace = F)
ols_clustered_model_t1t2 <- ols_clustered(dep.var="p_all",df=data_t1and2_long)
ols_clustered_model <- ols_clustered(dep.var="p_all",df=data_long)

screenreg(list(bezi_modelt1t2,ols_clustered_model$results,bezi_model,ols_clustered_model_t1t2$results),
       # custom.coef.map = list('mu (Intercept)' = 'Historical (Intercept)',
       #                        'mu timetime 2' = 'Present-day Change',
       #                        '(Intercept)' = 'Historical (Intercept)',
       #                        'timetime 2' = 'Present-day Change'
       #                        ),
       custom.model.names = c("BEZI","OLS","Full BEZI","Full OLS"),
       digits = 3,
       ci.force = T
       )



```

\begin{sidewaystable}[!htbp] \centering 
  \caption{Proximity to Public Lands} 
  \label{tab:pub_lands} 
\begin{tabular}{l c c c c }
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{Dependent Variable: Proximity to Public Lands} \\ 
\hline
 & BEZI & Full BEZI & OLS & Full OLS \\
\hline
Historical (Intercept)    & $-1.539^{***}$ &   $-1.592^{***}$        & $0.067^{***}$   &   $0.075^{***}$               \\
                     & $(-1.586;\ -1.492)$ &   $(-1.635;\ -1.549)$ &   $(0.051;\ 0.082)$    &   $(0.055;\ 0.094)$          \\
Present-day Change     & $0.506^{***}$     &   $0.519^{***}$         & $0.078^{***}$   &   $0.077^{***}$              \\
                     & $(0.388;\ 0.625)$   &   $(0.405;\ 0.633)$   &   $(0.045;\ 0.110)$   & $(0.044;\ 0.110)$            \\

\hline \\[-1.8ex]
Obs.           & 8165                & 10314              &  8165   &    10314               \\

\hline 
\hline \\[-1.8ex] 
\multicolumn{5}{l}{{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01}}
\end{tabular}


\end{sidewaystable} 









# References

Abatzoglou, J. T. (2013). Development of gridded surface meteorological data for ecological applications and modelling. International Journal of Climatology, 33(1), 121–131. https://doi.org/10.1002/joc.3413

Abatzoglou, J. T., & Williams, A. P. (2016). Impact of anthropogenic climate change on wildfire across western US forests. Proceedings of the National Academy of Sciences, 113(42), 11770–11775. https://doi.org/10.1073/pnas.1607171113

Dillon, Gregory K. 2018. Wildfire Hazard Potential (WHP) for the conterminous United States (270-m GRID), version 2018 classified. 2nd Edition. Fort Collins, CO: Forest Service Research Data Archive. https://doi.org/10.2737/RDS-2015-0046-2

Westerling, A. L., Hidalgo, H. G., Cayan, D. R., & Swetnam, T. W. (2006). Warming and Earlier Spring Increase Western U.S. Forest Wildfire Activity. Science, 313(5789), 940–943. https://doi.org/10.1126/science.1128834




