---
title: "Explore Difference in Gas Production"
date: '2019-02-25'
output: html_document
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)

```

## Setup Library
Install these packages if neccessary.
```{r project_setup, message = FALSE, warning = FALSE}

library(readr)
library(tidyr)
library(knitr)
library(DT)
library(dplyr)
library(stringr)
library(scales)
library(broom)
library(ggplot2)
library(ggbeeswarm)

```

## Data Preparation

### Load Data
Load the data imported, processed and saved from "data wrangle change score centroid and map data.R".
```{r}

load("~/Dropbox/__Papers_in_Progress/_Indian_Removal/_Data_and_R/x_Github/tribal_lands/R_Analysis/processed_data.RData")

```

### Prepare Data

Keep distinct records within each time point only because keeping all pairwise records will inflate the number of observations in time 1 and 2.
```{r}

data_long <- distinct(merged_data_record_all_long, tribe, time, FIPS, .keep_all = TRUE)

```

Create data.frame to include only tribes with time 1 and 2 data.
```{r}

data_t1and2_long <- filter(data_long, tribe %in% tribes_time1and2_lst$tribe)

```

**Check Data**
First, confirm the data is correct, each tribe should have 2 summarized records in total, one for time 1 and one for time 2, so the resulted data.frame should has 0 row.
```{r}
t1and2_lst <- group_by(data_t1and2_long, tribe, time) %>% 
  count() %>%
  ungroup() %>%
  group_by(tribe) %>%
  count() %>%
  filter(n < 2)

nrow(t1and2_lst)
```


## Exploratory Analyses

### Plot Gas Production by Time
### All Tribes, including those with time 1 or time 2 data only

* The distribution of gas production in time 1 and time 2 is skewed to the right, with notable outliers and zero-inflation.

#### All Data Histograms
```{r, message = FALSE, warning = FALSE}

#histogram
ggplot(data_long, aes(gas_avg, fill = time)) +
  facet_grid(rows = vars(time), scales = "free") +
  geom_histogram(position = "dodge", bins=75) + 
  theme_minimal()

#logged histogram (**IMPORTANT - Y-axis scales are dfferent..much lower time2)
ggplot(data_long, aes(gas_avg, fill = time)) +
  facet_grid(rows = vars(time), scales = "free") +
  geom_histogram(position = "dodge", bins=75) + scale_x_log10() + 
  theme_minimal()

#overlaid logged histogram
ggplot(data_long, aes(gas_avg, fill = time)) +
  geom_histogram(position = "dodge", alpha=0.5) + scale_x_log10() +
  theme_minimal()

# BOXPLOT
ggplot(data_long, aes(time, gas_avg, colour = time)) +
  geom_boxplot() +
  geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
  theme_minimal()

```


# AGGREGATE AVERAGE OF GAS ACROSS ALL TRIBES AT T1 to T2
```{r, message = FALSE, warning = FALSE}

# AGGREGATE MEAN, MAX... USING records_level data
data_long %>%
  group_by(time) %>%
  summarize(my_mean_gas = mean(gas_avg, na.rm=T), my_max_gas = max(gas_avg, na.rm=T), my_sum_gas = sum(gas_avg, na.rm=T))


# TRIBE_LEVEL.csv average change scores for each tribe
ggplot(merged_data_tribe, aes(tribe, avg_gas_change_score, label=NA)) +
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size=2))

```



## JUSTIN, CHANGE SCORE ANALYSIS
```{r}



```








#### Look at only those with gas production only, 90th percentile cutoff

* The distirbution of gas production is in general higher in time 2 compared to time 1 for tribes in counties with gas production only.

```{r, message = FALSE, warning = FALSE}

data_long_gas_only <- filter(data_long, gas_avg > 0)

# Histogram
ggplot(data_long_gas_only, aes(gas_avg, fill = time)) +
  facet_grid(rows = vars(time), scales = "free") +
  geom_histogram(position = "dodge") +
  theme_minimal() +
  xlim(0, quantile(data_long_gas_only$gas_avg, c(.90), na.rm = TRUE))

# Overlaid Histogram
ggplot(data_long_gas_only, aes(gas_avg, fill = time)) +
  geom_histogram(position = "dodge", alpha=0.5) +
  theme_minimal() +
  xlim(0, quantile(data_long_gas_only$gas_avg, c(.90), na.rm = TRUE)) +
  ylim(0,600)

# Boxplot
ggplot(data_long_gas_only, aes(time, gas_avg, colour = time)) +
  geom_boxplot() +
  geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
  theme_minimal() +
  ylim(0, quantile(data_long_gas_only$gas_avg, c(.90), na.rm = TRUE))

```





### Tribes with both time 1 or time 2 data

* The distribution of gas production in time 1 and time 2 is skewed to the right, with notable outliers and zero inflation.

#### All Data
```{r, message = FALSE, warning = FALSE}

ggplot(data_t1and2_long, aes(gas_avg, fill = time)) +
  facet_grid(rows = vars(time), scales = "free") +
  geom_histogram(position = "dodge") +
  theme_minimal()

ggplot(data_t1and2_long, aes(time, gas_avg, colour = time)) +
  geom_boxplot() +
  geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
  theme_minimal()


```


#### Look at only those with gas production only, 90th percentile cutoff

* The distirbution of gas is in general higher in time 2 compared to time 1 for tribes in counties with gas production only.

```{r, message = FALSE, warning = FALSE}

data_t1and2_long_gas_only <- filter(data_t1and2_long, gas_avg > 0)

ggplot(data_t1and2_long_gas_only, aes(gas_avg, fill = time)) +
  facet_grid(rows = vars(time), scales = "free") +
  geom_histogram(position = "dodge") +
  theme_minimal() +
  xlim(0, quantile(data_t1and2_long_gas_only$gas_avg, c(.90), na.rm = TRUE))  
  
ggplot(data_t1and2_long_gas_only, aes(time, gas_avg, colour = time)) +
  geom_boxplot() +
  geom_quasirandom(alpha = 1/10, varwidth = TRUE) +
  theme_minimal() +
  ylim(0, quantile(data_t1and2_long_gas_only$gas_avg, c(.90), na.rm = TRUE))

```

## Test for Significant Difference

### (1) Test for significant difference at the aggregate level

* Welch's t-test (t.test, paired = FALSE) is a parameteric test for two-sample mean comparisions that does not assume equal variance.
* Use Welch's t-test because the outcome gas production is a continous measures.
* Welch's t-test for dependent sample is not used because these are not true paired data, since we don't know which time 1 locations migrate to which time 2 locations and simply assume all possible migration routes happened.

### Use all records

```{r}

t.test(gas_avg ~ time, data = data_long, paired = FALSE)

```

```{r}

mean_t1 <- round(mean(filter(data_long, time == "time 1")$gas_avg, na.rm = T), 0)
mean_t2 <- round(mean(filter(data_long, time == "time 2")$gas_avg, na.rm = T), 0)
sd_t1 <- round(sd(filter(data_long, time == "time 1")$gas_avg, na.rm = T), 0)
sd_t2 <- round(sd(filter(data_long, time == "time 2")$gas_avg, na.rm = T), 0)
pvalue <- round(tidy(t.test(gas_avg ~ time, data = data_long, paired = FALSE))$p.value, 3)
tvalue <- round(tidy(t.test(gas_avg ~ time, data = data_long, paired = FALSE))$statistic, 3)
degreef <- round(tidy(t.test(gas_avg ~ time, data = data_long, paired = FALSE))$parameter, 3)

```

**Interpretation**

* At the aggregate level, the difference in gas production between time 1 (M = `r mean_t1` SD = `r sd_t1`) and time 2 (M = `r mean_t2`, SD = `r sd_t2`) was statistically signficant (t(`r degreef`)= `r tvalue`, `r ifelse(pvalue < .001, "p < .001", paste0("p = ", pvalue))`).

### Use only records where tribes have time 1 and 2 data

```{r}
t.test(gas_avg ~ time, data = data_t1and2_long, paired = FALSE)
```

```{r}

mean_t1 <- round(mean(filter(data_t1and2_long, time == "time 1")$gas_avg, na.rm = T), 0)
mean_t2 <- round(mean(filter(data_t1and2_long, time == "time 2")$gas_avg, na.rm = T), 0)
sd_t1 <- round(sd(filter(data_t1and2_long, time == "time 1")$gas_avg, na.rm = T), 0)
sd_t2 <- round(sd(filter(data_t1and2_long, time == "time 2")$gas_avg, na.rm = T), 0)
pvalue <- round(tidy(t.test(gas_avg ~ time, data = data_t1and2_long, paired = FALSE))$p.value, 3)
tvalue <- round(tidy(t.test(gas_avg ~ time, data = data_t1and2_long, paired = FALSE))$statistic, 3)
degreef <- round(tidy(t.test(gas_avg ~ time, data = data_t1and2_long, paired = FALSE))$parameter, 3)

```

**Interpretation**

* At the aggregate level for tribes with migration, the difference in gas production between time 1 (M = `r mean_t1` SD = `r sd_t1`) and time 2 (M = `r mean_t2`, SD = `r sd_t2`) was statistically signficant (t(`r degreef`)= `r tvalue`, `r ifelse(pvalue < .001, "p < .001", paste0("p = ", pvalue))`).


### (2) Test for significant difference at tribe level

```{r, message = FALSE, warning = FALSE}

no_test <- group_by(data_t1and2_long, tribe) %>%
do(tryCatch( {tidy(t.test(gas_avg ~ time, data = ., paired = FALSE))},
  error = function(e) {tidy(t.test(gas_avg ~ time, data = data_t1and2_long)) %>% mutate(estimate = NA)}
    ))

no_test[!!rowSums(is.na(no_test)),-1] <- NA

no_test <- no_test %>%
  filter(!is.na(p.value)) %>% 
  nrow()

```

This can only be tested with the `r nrow(tribes_time1and2_lst)` tribes where migrations occured. Furthermore, only tribes where gas production have changed between time points and with more than one data point at each time point can their differences be tested for statistical significance. This reduce the number of tribes from `r nrow(tribes_time1and2_lst)` to `r no_test`.

### Run Welch's t-test in Batch

* Run Welch's t-test in batch using group_by and do at the tribe level.
* Include a try call to catch error.
* Use tidy from broom package to format the results into a data.frame.
* Replace NA estimate with all NA for that comparison.

```{r, message = FALSE, warning = FALSE}

model <- group_by(data_t1and2_long, tribe) %>%
do(tryCatch( {tidy(t.test(gas_avg ~ time, data = ., paired = FALSE))},
  error = function(e) {tidy(t.test(gas_avg ~ time, data = data_t1and2_long)) %>% mutate(estimate = NA)}
    ))

model[!!rowSums(is.na(model)),-1] <- NA


```

Calculate number of test based only on tribes where there is non-zero difference in gas production between time 1 and 2.

```{r}

no_test <- nrow(filter(model, !is.na(p.value)))

```

* Create sig column to flag statistical significance results. 
* p-value cutoff is adjusted to control for Type I error due to multiple comparisons using Bonferroni correction (p value threshold = .05 / number of tests or `r no_test`), adjusted p-value threshold = `r .5/no_test`.

```{r, message = FALSE, warning = FALSE}

model <- model %>%
  mutate(sig = ifelse(p.value < .05 / no_test, "yes", "no"))

```

* Add average gas production, distance, and no of unique FIPS to help with interpretation
* Rename some variables for prettier column headers

```{r}

results_df <- inner_join(model, merged_data_tribe, by = "tribe") %>%
  mutate(`Avg Diff Gas` = avg_gas_avg_t2 - avg_gas_avg_t1) %>%
  select(tribe, sig, p.value, `Avg Diff Gas`, avg_gas_avg_t1, avg_gas_avg_t2, n_unique_FIPS_t1, n_unique_FIPS_t2, mid_dist) %>%
  arrange(p.value) %>%
  rename(
    `Avg Gas T1` = avg_gas_avg_t1,
    `Avg Gas T2` = avg_gas_avg_t2,
    `Unique FIPS T1` = n_unique_FIPS_t1,
    `Unique FIPS T2` = n_unique_FIPS_t2,
    `Mid Distance` = mid_dist)

```


### Results Table 
#### Ordered by p value in ascending order

```{r}

datatable(results_df,
          filter = "top",
          options = list(pageLength = 20)) %>%
   formatRound(columns = c('p.value'), digits = 3) %>%
   formatRound(columns = c('Avg Diff Gas', 'Avg Gas T1', 'Avg Gas T2', 'Mid Distance'), digits = 2)

```

```{r}

b_sig_tribe_lst <- filter(results_df, sig == "yes") %>%
  select(tribe)
sig_tribe_lst <- filter(results_df, p.value < .05) %>%
  select(tribe)

```

**Interpretation**

* The mean gas production comparisons for one tribe (`r b_sig_tribe_lst$tribe`) achieve statistical significance when the Bonferroni correction is used.
* The tests has low statistical power to detect differences given the number of observations at time 2 is much smaller than time 1.
* If Bonferroni correction is not used, gas production was significantly differ between time 1 and 2 for 7 tribes :(`r sig_tribe_lst$tribe`).
* Results with NA p values are from tribes where there isn't sufficient data points in both time point to perform the planned statistical tests (t-test).

**Overall Interpretation**

* Overall, a statistically significant difference was found at the aggregate level. At the tribe level, when correction for multiple comparisons was made, gas production for one tribe were found to be statistically differ between time 1 and time 2. Without correction, gas production was found to be statistically differ for 7 tribes.

* The lack of significant differences at the tribe level could be attributed to the low statistical power arises from the small number of observations at time 2. In some cases, there is only 1 data point in time 2 or time 1, which preclude the use of t-test to test for their mean differences.
